Implementation and assessment of tools for integrating forest roads into projections of the cumulative effects of disturbance on wildlife

### 2024-03-14 analysis/paper/paper.Rmd
playing with slope penalty options

```{r cost-tbl}
tbl <- "Cost Type|Value ($ per km)|Source
Slope|16178 + 504*slope|Interior appraisal manual
Major lakes|65000|Major water bodies of BC
Existing roads|0|Digital road atlas and forest tenure roads for BC
"
df <- read.delim(textConnection(tbl),header=FALSE,sep="|",strip.white=TRUE,stringsAsFactors=FALSE)
names(df) <- unname(as.list(df[1,]))
df <- df[-1,] # remove first row
row.names(df)<-NULL
knitr::kable(df, caption = "A simple model of road construction costs.")
```

>>>>

```{r cost-tbl}
tbl <- "Cost Type|Value ($ per km)|Source
Slope|16178 + 504*slope|Interior appraisal manual
Major lakes|NA|Major water bodies of BC
Existing roads|0|Digital road atlas and forest tenure roads for BC
"
df <- read.delim(textConnection(tbl),header=FALSE,sep="|",strip.white=TRUE,stringsAsFactors=FALSE)
names(df) <- unname(as.list(df[1,]))
df <- df[-1,] # remove first row
row.names(df)<-NULL
knitr::kable(df, caption = "A simple model of road construction costs.")
```
